\documentclass{article}

\usepackage{epsfig}  
\usepackage{amsmath} 
\usepackage{amssymb} 
\usepackage{amsthm}  
\usepackage{listings} 
\usepackage{color}
%\usepackage{enumerate}
\usepackage{enumitem}
\usepackage{multirow}
\usepackage{lastpage}
\usepackage{geometry}
\usepackage{fancyhdr}
\usepackage[all]{xy}
\usepackage{wrapfig}
\usepackage{listings}
\usepackage{url}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[justification=centering]{caption}
\usetikzlibrary{arrows}
\lstset{language=C, tabsize=4, basicstyle=\ttfamily}

\definecolor{light}{gray}{.75} 
\newtheorem{theorem}{Theorem}

\newcommand\etal{\emph{et al.}}

\pagestyle{fancy}
\lhead{CSCE 990} 
\chead{\bfseries PROJECT PROPOSAL V.2}
\rhead{Gerrard, Ore}
\lfoot{Gerrard, Ore}
\cfoot{\thepage\ of \pageref{LastPage}}
\rfoot{10 November 2014}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}

\hoffset 0pt
\voffset 0pt
\textwidth 15cm
\textheight 8.5in
\oddsidemargin 9pt
\marginparwidth 25pt
\setlength{\parindent}{0pt}
\setlength{\parskip}{.25cm}

%- - - - - - - - - - - - - - - - BEGIN DOCUMENT - - - - - - - - - - - - - - - - - - - 
\begin{document}



%\input{./target_problem_description.tex}
%\input{./sketch_of_technique.tex}
%\input{./expected_outcome.tex}
Instead of basing our spatial model on actions that may be unique to each system, we will now consider more general spatial properties.
We will be able to answer queries such as: ``can I get to this region of space?" (mobility), ``is the robot at a specified region within a specified time? or ever?" (location), ``do two robots occupy the same space at the same time?" (interference), ``does the robot stay within this specified space"? (containment) , ``is $robot_1$ ever $n$ units away from $robot_2$?" (separation/cohesion), and possibly more.

\begin{itemize}
  \item INPUT : multiple trace files of temporal-positional sensor readings of a robotic system performing a programmed task (alone or in tandem).

  \item OUTPUT : a list of properties such as: "$robot_1$ interferes with $robot_2$, $robot_1$ always remains below 3 meters", etc., grouped together either by robotic entity or by property.
\end{itemize} 
 
We partition the space into rectangular boxes and enumerate these to facilitate querying.
To check a property, we assume it is true, until a counterexample from the trace is found; then we may stop the search.
  
We will run initial tests using two UAVs in the NIMBUS lab flying tandem during a task.  We will see how adjusting parameters like the size of the box partitions and confidence-thresholds on properties affects the returned spatial models. 


\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,refs.bib}

\end{document}
