\documentclass{article}

\usepackage{epsfig}  
\usepackage{amsmath} 
\usepackage{amssymb} 
\usepackage{amsthm}  
\usepackage{listings} 
\usepackage{color}
%\usepackage{enumerate}
\usepackage{enumitem}
\usepackage{multirow}
\usepackage{lastpage}
\usepackage{geometry}
\usepackage{fancyhdr}
\usepackage[all]{xy}
\usepackage{wrapfig}
\usepackage{listings}
\usepackage{url}
\usepackage{tikz}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[justification=centering]{caption}
\usetikzlibrary{arrows}
\lstset{language=C, tabsize=4, basicstyle=\ttfamily}

\definecolor{light}{gray}{.75} 
\newtheorem{theorem}{Theorem}


\pagestyle{fancy}
\lhead{CSCE 990 - FALL 2014} 
\chead{\bfseries LOGIC}
\rhead{Gerrard, Ore}
\lfoot{Gerrard, Ore}
\cfoot{\thepage\ of \pageref{LastPage}}
\rfoot{23 November 2014}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0.4pt}

% JPO COMMANDS
\newcommand\etal{\emph{et al.}}
\newcommand\Z{\mathbb{Z}}
\newcommand\N{\mathbb{N}}


\hoffset 0pt
\voffset 0pt
\textwidth 15cm
\textheight 8.5in
\oddsidemargin 9pt
\marginparwidth 25pt
\setlength{\parindent}{0pt}
\setlength{\parskip}{.25cm}

%- - - - - - - - - - - - - - - - BEGIN DOCUMENT - - - - - - - - - - - - - - - - - - - 
\begin{document}

%\textbf{TYPES}\\
Given:\\
\begin{itemize}
    \setlength\itemsep{0.2em}
\item Time sequence $T =  \N \cup \{0\}, t \in T$\\
\item Graph $G = (V,E)$
\item S = $\mathbb{Z}^3$, with the identity equal to the size of the unit box.
\item b = Box.  a unit cube in S 
\item p = point in a trace 
\end{itemize}


Existence of box from trace point - give a point in space in the trace with point properties $x,y,z$ 
$$p_t \rightarrow (b_i | b_i^{xyz\_min} \leq p_t^{xyz} < b_i^{xyx\_max})$$

Existence of vertex from point
$$(p \rightarrow b_i) \rightarrow v_i, v_i \in V$$

Existence of directed edge from consecutive points
$$((p_t \rightarrow b_i) \land (p_{t+1} \rightarrow b_j) \land (i \neq j)) \rightarrow e(v_i, v_j) $$

Definition of Path
$$P ::  BOX, BOX \rightarrow \{0,1\}$$
$$P(b_a, b_z) = 1 \Leftrightarrow (\exists v_i | e(v_a, v_i) \land \exists \land e(v_i, v_j) \land e(v_j, v_z)) $$

Existence of turn
$$p_t \rightarrow (b_i | b_i^{xyz\_min} \leq p_t^{xyz} < b_i^{xyx\_max})$$
%$$3\ \ \ \ h \leftarrow max(max-list(conf-set[i]),max-list(past-fc[i]))$$

\newpage
\textbf{PROPERTIES}\\
SINGULAR\\
\begin{itemize}
\item Can an actor return to its home?  There exists a path from $home$ to $home$.  
  $$\phi_{\{returnhome\}} = \exists P(b_{home}, b_{home})$$
  %$$\phi_{\{go,home\}} = \exists P(b_{home}, b_{home}) \models a_{returnhome}$$ 
\item Can an actor move to multiple places? There exists a path from home to at least two places.
  $$\phi_{\{multiplePlaces\}} = \exists (P(b_{home}, b_a), P(b_{home}, b_b)| b_a \neq b_a)$$

\item Does the trace have no repetition? For all edges in $G$, all destinations are different.
  $$\phi_{\{noRepetition\}} = \forall e(v_a, v_b), e(v_c,v_d) in E, v_b \neq v_c, v_a \neq v_d$$

\item Does an actor return to a box? There exists a path from a box to that same box.
  $$\phi_{\{pathCycle\}} = \exists P_{ab}, P_{cd} | a = d$$
\item Can an actor teleport? Does there exist an edge from two `non adjacent boxes'  (Define adjacents?)
  $$\phi_{\{teleport\}} = \exists  p_t, p_{t+1} | \lnot Adjacent(b_{p_t}, b_{p_{t+1}})$$
\item Does an actor have a $n$ hot box? 
  $$\phi_{\{hotBoxOfSizeN\}} = \exists b_i, v_i \in E | n \geq |\{e \in E | e(v_x, v_i), v_x \in E\}$$
  (Question : our graph can't capture multiple visits?)
\item Does an actor have a $n$ hot path? (pheremone)\\
  (Question : our graph can't capture multiple visits?)
\item Can an actor move backwards?
  $$\phi_{\{movebackwards\}} = $$
  (Question : define directionality)
\item What is the longest path in one continuous direction?
  $$\phi_{\{\}} = $$
\item Is the actor confined to a plane?
\item what is the total number of visited voxels?
\item path happens before another path
\end{itemize}

MULTI-TRACE, SINGLE ACTOR\\
\begin{itemize}
  \item Which voxel is visited most (if any)?
  \item 
\end{itemize}

MULTIPLE SIMULTANEOUS ACTORS\\
\begin{itemize}
  \item Do two actors paths intersect with an $n$-sized neighborhood?
  \item 
\end{itemize}

% 17 NOV


\end{document}
